The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-12 paper/ms.tex
finishing table2.
Lambda errors added

The central result of this paper is summarized in Figure
\ref{fig:differentvelocities}. It shows the evident
impact of rotation on the morphology of the emergent \ly line.
The panel focus on the results for all of our symmetric models
 $\tau_{H}=10^{6}, 10^{6}, 10^{5}$, showing that the
influence of rotation is present both when the photons are either
homogeneously or centrally initialized over the gas volume.

@@

There are three clear effects on the line's morphology as the
rotational veloctiy increases. First, the line
broadens; second, the double peaks reduce their intensity; and third,
the intensity at the line center rises. The two last effects give the
impresion that the double peaks are merger into one at high rotational
velocities, a result that is evident for the homogeneously distributed
sources as shown in right panel in Figure \ref{fig:differentvelocities}.

We use the full width at half maximum (FWHM) to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how $FWHM$ increases
with rotational velocity both for the central an homogeneous source
distributions.  We parameterize the dependency of the linewidth as
\begin{equation}
 FWHM^2 = FWHM_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where $FWHM_{0}$ is the
velocity width in the static case and $\lambda$ is a positive scalar
to be determined as a fit to the data. With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.9 \pm$ and $\lambda_{\rm h}=
1.9\pm $ respectively.

@@

In Figure \ref{fig:Nscatt} we show the average number of scatterings
$\langle N_{\rm scatt}\rangle$ as a function of the rotational velocity
$V_{\rm max}$. For the central source distribution the average number of
scatterings $\langle N_{\rm   scatt}\rangle$ changes less than $0.5\%$
for different velocities. In this setup the number of scatterings is
proportional to the optical depth, with $\langle N_{\rm
  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depth
values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$, respectively

@@

In this case we find that for a static sphere $\langle N_{\rm
  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this
representsfactors of $(0.66, 0.59, 0.55)$ lower than the centrally
emitted photons. In contrast the analytic solution for the homogeneous
slab gives $0.72$ times less scatterings in the homogeneous case than
in the central one.

In order to gain a deeper understanding of these results and explain
the results for the maxima in the line morphology we make 2D
histograms for the number of scatterings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
such histogram in the case $\tau_{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x$-$N_{\rm scatt}$.

@@

\begin{table}
\begin{center}
\begin{tabular}{c c}
\hline \hline
Model, $\tau_{H}$ & $\ V_{max}(km\ s^{-1})$ $0, 50, 100, 200, 300$ \\
\hline \hline
Homogeneous $10^{5}$& $0.2637, 0.2661, 0.3091, 0.3570, 0.3709$ \\
Homogeneous $10^{6}$ & $0.2894, 0.2891, 0.3096, 0.3607, 0.3937$ \\
Homogeneous $10^{7}$ &$ 0.2279, 0.2298, 0.2318, 0.2547, 0.2813 $\\
Central $10^{5}$ & $0.0966, 0.0966, 0.0965, 0.0965, 0.0965$ \\
Central $10^{6}$ & $0.0663, 0.665, 0.0665, 0.0665, 0.665$ \\
Central $10^{7}$ & $0.0149, 0.0158, 0.0158, 0.0158, 0.0158$ \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
fraction as a function of the rotational velocity. The curves for the
central source distribution stay flat, while for the homogeneous case
there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
the models with low optical depth. For instance, in models with
$\tau_{\rm H}=10^5$, the static scape fraction is $0.26$ and increases
to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
all the values for the escape fraction {\bf We also need a table
  listing the escape  fraction values.}

>>>>

The central result of this paper is summarized in Figure
\ref{fig:differentvelocities}. It shows the evident
impact of rotation on the morphology of the emergent \ly line.
The panel focus on the results for all of our symmetric models
 $\tau_{H}=(10^{6}, 10^{6}, 10^{5}$), showing that the
influence of rotation is present both when the photons are either
homogeneously or centrally initialized over the gas volume.

@@

There are three clear effects on the line's morphology as the
rotational veloctiy increases. First, the line
broadens; second, the double peaks reduce their intensity; and third,
the intensity at the line center rises. The two last effects give the
impresion that the double peaks are merger into one at high rotational
velocities, a result that is evident for the homogeneously distributed
sources as shown in the dashed lines of Figure \ref{fig:differentvelocities}.

We use the full width at half maximum (FWHM) to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how $FWHM$ increases
with rotational velocity both for the central an homogeneous source
distributions.  We parameterize the dependency of the linewidth as
\begin{equation}
 FWHM^2 = FWHM_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where $FWHM_{0}$ is the
velocity width in the static case and $\lambda$ is a positive scalar
to be determined as a fit to the data. With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.9 \pm 3.17\times 10^{-17}$ and $\lambda_{\rm h}=
1.9\pm 3.07\times 10^{-10}$ respectively.

@@

In Figure \ref{fig:Nscatt} we show the average number of scatterings
$\langle N_{\rm scatt}\rangle$ as a function of the rotational velocity
$V_{\rm max}$. For the central source distribution the average number of
scatterings $\langle N_{\rm   scatt}\rangle$ changes less than $0.5\%$
for different velocities. In this set-up the number of scatterings is
proportional to the optical depth, with $\langle N_{\rm
  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depth
values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$, respectively

@@

In this case we find that for a static sphere $\langle N_{\rm
  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this
represents factors of $(0.66, 0.59, 0.55)$ lower than the centrally
emitted photons. In contrast the analytic solution for the homogeneous
slab gives $0.72$ times less scatterings in the homogeneous case than
in the central one.

In order to gain a deeper understanding of these results and explain
the results for the maxima in the line morphology we make 2D
histograms for the number of scatterings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
such histograms in the case $\tau_{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x$-$N_{\rm scatt}$.

@@

\begin{table}
\begin{center}
\begin{tabular}{c c}
\hline \hline
Model, $\tau_{H}$ & $\ V_{max}(km\ s^{-1})$ $0, 50, 100, 200, 300$ \\
\hline \hline
Homogeneous $10^{5}$& $0.2637, 0.2661, 0.3091, 0.3570, 0.3709$ \\
Homogeneous $10^{6}$ & $0.2894, 0.2891, 0.3096, 0.3607, 0.3937$ \\
Homogeneous $10^{7}$ &$ 0.2279, 0.2298, 0.2318, 0.2547, 0.2813 $\\
Central $10^{5}$ & $0.0966, 0.0966, 0.0965, 0.0965, 0.0965$ \\
Central $10^{6}$ & $0.0663, 0.665, 0.0665, 0.0665, 0.665$ \\
Central $10^{7}$ & $0.0149, 0.0158, 0.0158, 0.0158, 0.0158$ \\
\hline
\end{tabular}
\caption{
 Escape fraction values for all of the models. } 
\label{table:escape}
\end{center}
\end{table}

@@

Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
fraction as a function of the rotational velocity. The curves for the
central source distribution stay flat, while for the homogeneous case
there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
the models with low optical depth. For instance, in models with
$\tau_{\rm H}=10^5$, the static scape fraction is $0.26$ and increases
to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
all the values for the escape fraction.
